Copulas and their potential for ecology

### 2019-10-15 Paper.Rmd
fig edited
changes to acknowledgments

We thank Joel E. Cohen for making us aware of copulas and their potential utility in the 
first place. We thank the many contributors to the large datasets 
we used; D. Stevens and P. Verrier for data 
extraction; and David Tilman, Lauren Hallet, Jonathan Walter, Thomas 
Anderson, Lei Zhao, and editors and annonymous reviewers for helpful suggestions. 
We thank James Bell of the Rothamsted Insect Survey (RIS). 
The RIS, a UK Capability, is funded by the Biotechnology and Biological Sciences Research Council 
under the Core Capability Grant BBS/E/C/000J0200. SG, LWS and DCR were partly funded by US National 
Science Foundation grants 1714195 and 1442595 and the James S McDonnell Foundation.

>>>>

We thank Joel E. Cohen for making us aware of copulas and their potential ecological utility in the 
first place. We thank the many contributors to the large datasets 
we used; D. Stevens and P. Verrier for data 
extraction; and David Tilman, Lauren Hallet, Jonathan Walter, Thomas 
Anderson, Lei Zhao, Andrew Rypel, and editors and annonymous reviewers for helpful suggestions. 
We thank James Bell of the Rothamsted Insect Survey (RIS). 
The RIS, a UK Capability, is funded by the Biotechnology and Biological Sciences Research Council 
under the Core Capability Grant BBS/E/C/000J0200. SG, LWS and DCR were partly funded by US National 
Science Foundation grants 1714195 and 1442595 and the James S McDonnell Foundation.
